Territoriality and the organization of technology during the Last Glacial Maximum in southwestern Europe

### 2019-12-12 analysis/paper/SOM3.Rmd
paper out

cores_table <- tabmulti(cores_tidy, "Context", var_list,
                 p.include = FALSE,
                 n.headings = FALSE,
                 bold.varnames = TRUE,
                 bold.colnames = TRUE,
                 ynames = c(CoreType = "Core type", Platforms = "Platforms", CoreSection = "Core section", BlankType = "Blank type", CortexPerc = "Cortex %", Weight = "Weight", Elongation = "Elongation", Flattening = "Flattening"))

>>>>

cores_table <- tabmulti(cores_tidy, "Context", var_list,
                 p.include = FALSE,
                 n.headings = FALSE,
                 latex = TRUE,
                 bold.varnames = TRUE,
                 bold.colnames = TRUE,
                 ynames = c(CoreType = "Core type", Platforms = "Platforms", CoreSection = "Core section", BlankType = "Blank type", CortexPerc = "Cortex %", Weight = "Weight", Elongation = "Elongation", Flattening = "Flattening"))
